Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-01-05 writing/CONUS_AOD.qmd
Converted a code block to inline code.

```{r error_envelope_AMT2018}
# error envelope for MAIAC is equivalent to that reported in AMT MAIAC publication
dt[, round(100 * mean(y.sat > (y.ground - 0.05 - 0.1*y.ground) & y.sat < (y.ground + 0.05 + 0.1*y.ground)))][1]
```

>>>>

The original error envelope (reported in the AMT MAIAC publication) had `r dt[, round(100 * mean(y.sat > (y.ground - 0.05 - 0.1*y.ground) & y.sat < (y.ground + 0.05 + 0.1*y.ground)))][1]`% coverage in our data.
